Arjun Shanmugam's Senior Thesis

### 2022-12-23 writing/paper/main.tex

\documentclass{article}
\usepackage{graphicx, setspace, booktabs, float, xcolor, rotating, lscape, lscape, sectsty, rotating, pdflscape}
\usepackage[utf8]{inputenc}
\usepackage[letterpaper, portrait, margin=0.8in]{geometry}
\usepackage[shortlabels]{enumitem}
\usepackage[round, sort]{natbib}

@@

\title{Thesis Updates}
\author{Arjun}
\date{December 2, 2022}

\maketitle
\input{output/01_exploratory/tables/summary_statistics.tex}

\begin{landscape}
\input{output/01_exploratory/tables/balance_table.tex}
\end{landscape}

\input{output/01_exploratory/tables/total_val_results_table.tex}
\input{output/01_exploratory/tables/bldg_val_results_table.tex}
\input{output/01_exploratory/tables/placebo_first_stage.tex}
\end{document}

>>>>

\documentclass[12pt]{article}

\usepackage{amssymb,amsmath,amsfonts,eurosym,geometry,ulem,graphicx,caption,color,setspace,sectsty,comment,footmisc,caption,natbib,pdflscape,subfigure,array,hyperref}

\normalem

\onehalfspacing
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}{Proposition}
\newenvironment{proof}[1][Proof]{\noindent\textbf{#1.} }{\ \rule{0.5em}{0.5em}}

\newtheorem{hyp}{Hypothesis}
\newtheorem{subhyp}{Hypothesis}[hyp]
\renewcommand{\thesubhyp}{\thehyp\alph{subhyp}}

\newcommand{\red}[1]{{\color{red} #1}}
\newcommand{\blue}[1]{{\color{blue} #1}}

\newcolumntype{L}[1]{>{\raggedright\let\newline\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\arraybackslash\hspace{0pt}}m{#1}}

\geometry{left=1.0in,right=1.0in,top=1.0in,bottom=1.0in}

\begin{titlepage}
\title{Arjun Shanmugam's Senior Thesis}
\author{Arjun Shanmugam}
\date{\today}
\maketitle
\begin{abstract}
\noindent Placeholder\\

\bigskip
\end{abstract}
\setcounter{page}{0}
\thispagestyle{empty}
\end{titlepage}
\pagebreak \newpage

@@

\section{Introduction} \label{sec:introduction}

\section{Literature Review} \label{sec:literature}

\section{Data} \label{sec:data}
    \subsection{Evictions Data}
    \subsection{Tax Assessment Records}
    \subsection{Zestimates}
    \subsection{Summary Statistics}
        \begin{table}[]
            \centering
            \begin{tabular}{c|c}
                 &  \\
                 & 
            \end{tabular}
            \caption{Caption}
            \label{tab:my_label}
        \end{table}

\section{Results} \label{sec:result}

\section{Discussions} \label{sec:discussion}

\section{Conclusion} \label{sec:conclusion}

\singlespacing
\setlength\bibsep{0pt}
\bibliographystyle{my-style}
\bibliography{Placeholder}

\clearpage

\onehalfspacing

\section*{Tables} \label{sec:tab}
\addcontentsline{toc}{section}{Tables}

\clearpage

\section*{Figures} \label{sec:fig}
\addcontentsline{toc}{section}{Figures}

\clearpage

\section*{Appendix A. Placeholder} \label{sec:appendixa}
\addcontentsline{toc}{section}{Appendix A}

\end{document}
